Supplemental Materials for ``Universals of word order result from optimization of grammars for efficient communication''

### 2019-05-16 second-draft/pnas-word-order-si.tex
si

@@

>>>>

\paragraph{Per-Language Results}
Figure~\ref{fig:pareto-per-lang}

\begin{figure}[ht]
\centering
\includegraphics[width=\textwidth]{../results/plane/pareto-plane-perLanguage.pdf}
\caption{per language results. Green: random baselines, Red: real grammar, blue: approximate Pareto frontier, computed from the optimized grammars.\textcolor{red}{would be good to have same colors as in main paper} All data are $z$-transformed.}\label{fig:pareto-per-lang}
\end{figure}

@@

\section{Other (Preregistered) Experiments}

Here we report the results of prior preregistered simulation runs.

\begin{table}[ht]
\begin{tabular}{|c|ccc|c}
	%&
& $\lambda=1.0$ & $\lambda=0.9$ & $\lambda=0.9$ \\ \hline \hline 
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {1}}}}		  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_lifted_case.pdf}     } 
 		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_lifted_case.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_lifted_case.pdf}     }  \\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {2}}}}	 
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_lifted_cop.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_lifted_cop.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_lifted_cop.pdf}     }  \\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {3}}}}	 
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_aux.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_aux.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_aux.pdf}     }  \\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {4}}}}	
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_nmod.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_nmod.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_nmod.pdf}     }  \\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {5}}}}	 
			&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_acl.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_acl.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_acl.pdf}     }  \\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {6}}}}	
			&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_lifted_mark.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_lifted_mark.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_lifted_mark.pdf}     }  \\
&&&\\ \hline
	\multirow{2}{*}{	\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {7}}}}	
			&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_obl.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_obl.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_obl.pdf}     }  \\
&&&\\ \hline
	\multirow{2}{*}{\raisebox{.5pt}{\textcircled{\raisebox{-.9pt} {8}}}}	
			&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first10_Efficiency_xcomp.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_first09_Efficiency_xcomp.pdf}     }  
		&   \multirow{2}{*}{  \includegraphics[width=0.06\textwidth]{../results/correlations/figures/posteriors/posterior_Efficiency_xcomp.pdf}     }  \\
&&&\\ \hline
	\end{center}
\caption{Previous experiment with $\lambda=0.9$ (Preregistration)}\label{table:corr-resu}
\end{table}
